Sweep A - general experiment analysis.

### 2018-04-04 voltagebudget/analysis/freq_analysis.Rmd
Cleanup freq analysis more

results %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    V_b = mean(V_b),
    V_osc = mean(V_osc),
    delta_spikes = mean(delta_spikes),
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances_pop = mean(variances_pop),
    variances = mean(variances)) -> avg_results

@@

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>%
  filter(As < 0.05e-9) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.5, alpha=0.5) + 
  labs(x="As (namp)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

@@

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x="V_osc/V_comp", y="Variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  theme_classic() +
  lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

>>>>

results %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    V_b = mean(V_b),
    V_osc = mean(V_osc),
    n_spikes = mean(n_spikes),
    delta_spikes = mean(delta_spikes),
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances_pop = mean(variances_pop),
    variances = mean(variances)) -> avg_results

@@

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>%
  filter(As < 0.05e-9) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.5, alpha=0.5) + 
  labs(x="As (namp)", y="Deviation (ms)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>%
  filter(As < 0.05e-9) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=As*1e9, y=(variances_pop/n_spikes)*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.5, alpha=0.5) + 
  labs(x="As (namp)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

@@

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x="V_osc/V_comp", y="Deviance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  theme_classic() +
  lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  ggplot(aes(x=V_osc/V_comp, y=(variances_pop/n_spikes)*1e3, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x="V_osc/V_comp", y="Variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```
